Progress Report

### 2020-09-04 documentation/Optimization Work/08_27_20.tex
optimization test working and figured out why steps always improve

	We classify the terms of the resulting polynomial into two types:
	cross types (e.g $(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$) and non-cross terms (e.g $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$). For non-cross terms, the phases will always cancel out ($\phi_i \phi_i^H = 1$). For the cross-terms, note that
	for each term in the polynomial, the hermetian of the term is also in the polynomial sum (e.g both $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$ and $ (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}\mG^H$). Because $trace(\mH^H) = trace(\mH)^*$, the complex component of these terms will always cancel. In the case of minimizing the MSE, this means that we want to minimize the resulting real component for all of these cross terms. In order to investigate further, we decompose the problem further. Neglecting the non-cross terms and using the linearity of the $trace$ operator with respect to scaling, we can equivalently consider the problem 

@@

	    \underset{\phase}{\text{maximize }}
	    & \; Img \left( \Sigma_{i=1}^{K} \Sigma_{j=i}^{K} c_{i,j} \phi_{i} \phi_{j}  \right)

@@

	    | \phi_i | = 1  \forall i \in {1 \cdots	 K}.
	\end{align}\label{mse_problem_clear}
	Note that because the polynomial in Problem \eqref{mse_problem} is the trace of a Hermetian product, only the imaginary component along the diagonal of each cross term is canceled by its corresponding Hermetian component in the sum. Replacing $ Img$ with a trigonometric function it is clear that this utility function is non-convex over the domain.
\section{Phase Optimization}
One potential method of performing this optimization is based on the ideas of coordinate descent in which a single variable is updated while all others are held constant.
From problem \eqref{mse_problem_clear} it is clear that if all $\phi_{j} \; j \neq i $ are held constant,$\phi_{j} \; j \neq i $can be chosen as a phase which fulfills the objective function. 
For a given step of this algorithm in which $\phi_{i}$ the update is determined by a sum $\phi_{i}a + b$ and $\phi_{i}$ is chosen so at to maximize the 
complex component of the sum (which we will be canceled out by its complex conjugate.
The numerical results below indicate the impact of this optimization technique on the MSE of the IRS system described above.

\begin{enumerate}
\item
	Always compare to the matched filter with random phases
\end{enumerate}
\bibliography{bibliography}
\end{document}

>>>>

	Expanding the above utility function and neglecting the terms without any phase coefficients, the above utility function becomes
	\Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right ) +  \Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right)^H.
	From this expression it can be seen that the complex component of each term will be canceled by its complex conjugate.
	One method to potentially perform this optimization is to iterate over each element of the IRS and choose $\phi_{i}$ such that 
	the resulting components of the sum have entirely negative and real. In this case, each step of the algorithm solves the problem

@@

	    \underset{\phi_k}{\text{minimize }}
	    & \; \phi_k c + \phi_k^* c^* + a 

@@

	    | \phi_i | = 1   \; \forall i \in {1 \cdots	 K}
	in which $a \in \reals$ and $c \in \complex$ so the result is simply to choose $\phi_k$ to make $\phi_k c$ negative and real.
	The primary difficulty to performing such and optimization is finding the all values of $ c_i $ for each $\phi_{k}$ as each phase will be associated with 
	more than one $ c_i $ (particularly in the case of the matched filter precoder).
\section{Optimization Implementation}
To begin solving this problem I considered randomly selecting many complex numbers and corresponding phases in order to model the utility function 
	\Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right ) +  \Sigma_{i=1}^{N} \left(\prod_{k=1}^{M_i}\phi_{k} c_i \right)^H.
	The algorithm then iterates through each $\phi_{k}$ shifts the phase such that the result is a negative real (only if this update improves the utility function).
\bibliography{bibliography}
\end{document}
